Empirical normative theories

### 2020-06-23 simple.tex
Started clarif. falsif.

\begin{proposition}
	An empirical theory has only finite sets $\gargs[i, \phi]$, and an upper bound on their size exists that is independent of ${\ileadsto}$.
\end{proposition}
\begin{proof}
	Given $i, \phi$. Observe that $\forall \ard: d^{i, \phi}(\ard) \subseteq {\gbeatsmt}(\ard)$. Thus, $d^{i, \phi}$ is finite. Also, the transitive closure through $\sigma^i$ changes a finite number of time, otherwise it is possible to build an infinite chain in ${\gbeatsmt}$.
\end{proof}

@@

Define the crossing of $\args_{j-2}, \argsd_j \subseteq \allargs$ as $\args_j = \set{\ar_{j-2} + \ard_j \suchthat \ar_{j-2} \in \args_{j-2}, \ard_j \in {\gbeatsmt}(\ar_{j-2}) \cap \argsd_j}$.
\begin{definition}[Convincingness (outdated)]
	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \exists k \in 2\N$ and finite sequences $(\args_j)_{j \in 2\N, j ≤ k}, (\argsd_j)_{j \in 2\N^*, j ≤ k}$ such that:
	\begin{itemize}
		\item $\emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$;
		\item $\forall j \in 2\N^*, j ≤ k: \argsd_j \subseteq {\gbeatsmt}(\args_{j-2})$;
		\item $\forall j \in 2\N^*, j ≤ k: \args_j$ is the crossing of $\args_{j-2}, \argsd_j$;
		\item $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under d-protection of $\argsd_{j + 2}$ (defining $\argsd_{k + 2} = \emptyset$).
	\end{itemize}
\end{definition}

Now prove that Convincingness is the same thing as requiring that the elements be selected exactly when $\ar_1$ attacks $\ar_0$ (with single-try models).

@@

A falsification instance of an empirical theory is a tuple $(i, \phi, \ar, \ard, \hist)$ such that $(\phi, \ar, \ard) \in \gargs[i, \phi]$ and, defining $\ar_0 = \ar + \ard$: $[{\gbeatsinv}(d^{i, \phi}(\ard)) \cap \hist = \emptyset] \land [\hist \ibeatse[!\phi] \ar_0]$ (the theory says that this history should defend $\phi$ under prot of something and that is not in the history).

>>>>

\subsection{Falsifiability}
\begin{proposition}
	An empirical theory has only finite sets $\gargs[i, \phi]$, and an upper bound on their size exists that is independent of ${\ileadsto}$.
\end{proposition}
\begin{proof}
	Given $i, \phi$. Observe that $\forall \ard: d^{i, \phi}(\ard) \subseteq {\gbeatsmt}(\ard)$. Thus, $d^{i, \phi}$ is finite. Also, the transitive closure through $\sigma^i$ changes a finite number of time, otherwise it is possible to build an infinite chain in ${\gbeatsmt}$.
\end{proof}

@@

@@

A falsification instance of an empirical theory is a tuple $(i, \phi, \ar, \ard, \hist, \ar_1)$ such that $(\phi, \ar, \ard) \in \gargs[i, \phi]$ and, defining $\ar_0 = \ar + \ard$: $[{\gbeatsinv}(\ard) \cap \hist = \emptyset] \land [\hist \text{ ends with } \set{\ar_1, \ar_0}] \land \ar_1 \ibeatse[!\phi] \ar_0]$ (the theory says that this history should defend $\phi$ under prot of something and that is not in the history).
